[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting and intermittent phase-locking

### 2016-07-18 article/detorakis-2016.tex
Corrections after second review round

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting
        and intermittent phase-locking
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
\usepackage{array}

@@

This work introduces a reference implementation of a neuron model 
for thalamocortical relay neurons, \cite{wang:1994} proposed by X-J Wang.
The model is conductance-based and takes advantage of an interplay between 
a T-type calcium current and a non-specific cation sag current and thus it
is able to generate spindle and delta rhythms. Another feature of this model
is the presence of an intermittent phase-locking phenomenon
where action potentials of sodium take place in a non-periodic manner, despite
the fact that they are phase-locked to the periodic input current. Finally,
the model is capable of generating tonic spike patterns. The reference 
implementation in this work, does not aim to reproduce all the results of 
the original article, but some of them in order to test if the model can be
easily reproduced and at what degree the original results are reproducible.
The source code of reference implementation is written in Python (Numpy,
Scipy and Matplotlib).

@@

The model is described in this section following the paradigm of 
Nordlie et al, \cite{nordlie:2009}. Therefore, a brief description of
the model, equations, parameters and inputs are given in the form of 
tables.

Table~\ref{Table:1} provides a description of the model and Table~\ref{Table:2}
gives a glimpse of the input used during simulations. Table~\ref{Table:3}
introduces the equations of the model. The neuron model is conductance-based
consisting in four differential equations describing the dynamics of membrane
potential and the kinetics of a T-Type calcium current, a Sag current channel
and a Potassium channel. The rest currents are described by algebraic
equations. Finally, all simulations parameters are given in
Table~\ref{Table:5} and the simulations times can be found in
Table~\ref{Table:2}.

The reference implementation has been done in a Python class (Python $3.5.1$)
along with Numpy (version $1.10.4$), Scipy (version $0.17.0$) and Matplotlib
($1.5.1$). The numerical integration has been done by the \emph{ode} method 
of Scipy \emph{integrate} package taking advantage of the BDF multistep method
\cite{ascher:1998}. This is a diversion from the original implementation, since
in \cite{wang:1994}, the author has numerically integrated the system of 
the four ODEs by using a fifth-order adaptive size Runge-Kutta method. This
could cause some of the numerical deviations we noticed during the
implementation of the model. The values for the input current must be 
slightly elevated in order to achieve exactly the same results as
in the original implementation.

All the simulations ran on a Dell OptiPlex $7040$, equipped with a sixth
generation i$7$ processor, $8$GB of physical memory and running Arch Linux
as operating system. The total execution time of simulations is $38.76$
seconds and the total consumed memory is $66$MB. Table~\ref{Table:3}, shows
all the parameters we used in order to produce our results (see Results). 
No any other implementation of this model found by the authors in order 
to make any further comparison with.  
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- one neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Hodgkin-Huxley conductance-based \\\rowcolor{Gray}
        Channel Models & \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or periodic rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, channels activation, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{Table:1}
\end{table}
 %%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ccc}
        \thickhline
        \multicolumn{3}{c}{Simulation Time} \\ \thickhline
        Figure & Simulation Time ($ms$) & Integration Step ($ms$) \\ \rowcolor{LightGray}
        $1$ & $6000$ & $0.05$ \\ \rowcolor{Gray}
        $2$ & $2000$ & $0.05$ \\ \rowcolor{LightGray} 
        $3$ & $6000$ & $0.05$  \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Time.}}
    \label{Table:2}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{llcccc}
        \thickhline
        \multicolumn{6}{c}{Input} \\\thickhline
        Figure  & Type & Form & \parbox[t]{1.5cm}{Frequency
            ($\frac{1}{P_0}$,$Hz$)} & 
            \parbox[t]{1.5cm}{Duration ($p$, $ms$)} &
            \parbox[t]{1.5cm}{Amplitude ($\mu A / cm^2$)} \\
        \thickhline \rowcolor{LightGray}
        Figure~$1$ & Periodic & 
            \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} &
            \parbox[t]{1.1cm}{$5$, $8$, $10$} &
            \parbox[t]{1.1cm}{$10$, $40$, $75$, $120$} &
            \parbox[c]{0.3cm}{$-1.0$}
            \\\rowcolor{Gray}
        Figure~$2$ & Constant  & 
        \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
        -- & -- & \parbox[c]{0.3cm}{$+3.0$ \\ $0.0$ $-0.5$ $-0.55$ $-0.6$ $-0.8$
        $-1.3$ $-2.1$} 
        \\\rowcolor{LightGray}
        Figure~$3$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$-0.95$} \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the applied current
        $I_{\text{app}}$ }}
    \label{Table:3}
\end{table}
%%

\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{1.5cm}ll}
        \thickhline
        \multicolumn{2}{c}{Neuron Model} \\\thickhline
        \rowcolor{Gray}
        Name  &  Thalamocortical relay neuron  \\ \rowcolor{LightGray}
        Type  &  Conductance-based neuron  \\ \rowcolor{Gray}
        Membrane Potential & $
            \begin{aligned}
                C_m \frac{dV(t)}{dt} &= -I_T - I_h - I_{Na}
                  - I_K - I_{Na(P)} - I_L + I_{\text{app}}
              \end{aligned}$ \\ \rowcolor{LightGray}
        T-Type Calcium Current ($I_T$) & $
            \begin{aligned}
                I_T &= g_T \cdot s^3_{\infty}(V)\cdot h \cdot (V-V_{Ca}) \\
                s_{\infty}(V) &= \frac{1}{1 + \exp(-\frac{V+65}{7.8})} \\
                \frac{dh(t)}{dt} &= \phi_h \frac{h_{\infty}(V) - h}{\tau_h(V)} \\
                h_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V-\theta_h}{k_h})} \\
                \tau_h(V) &= h_{\infty}\exp(\frac{V+162.3}{17.8}) + 20
            \end{aligned} $
            \\ \rowcolor{Gray}
        Sag Current ($I_h$) & $
            \begin{aligned}
                I_h &= g_h \cdot H^2 \cdot (V-V_h) \\
                H_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V+69}{7.1})} \\
                \frac{dH(t)}{dt} &= \phi_H \frac{H_{\infty}(V) - H}{\tau_H(V)} 
            \end{aligned} $
            \\ \rowcolor{LightGray} 
        Hodgkin-Huxley Currents ($I_K$) and ($I_{Na}$) & $
            \begin{aligned}
                I_{K} &= g_K \cdot n^4 \cdot (V - V_K) \\
                \frac{dn(t)}{dt} &= \phi_n \frac{n_{\infty}(V) - n(t)}{\tau_n(V)} \\
                n_{\infty}(\sigma_K, V) &= \frac{\alpha_n(\sigma_K, V)}
                        {\alpha_n(\sigma_K, V) + \beta_n(\sigma_K, V)} \\
                \tau_n(\sigma_K, V) &= \frac{1}{\alpha_n(\sigma_K, V)
                        + \beta_n(\sigma_K, V)} \\
                \alpha_n(\sigma_K, V) &= \frac{-0.01 (V + 45.7 - \sigma_K)}
                {\exp(-0.1(V + 45.7 - \sigma_K)) - 1} \\ 
                \beta_n(\sigma_K, V) &= 0.125 \exp(-\frac{V + 55.7 -
                \sigma_K}{80}) \\
                I_{Na} &= g_{Na} \cdot m^3_{\infty}(\sigma_{Na}, V)
                    \cdot (0.85 - n) \cdot (V - V_{Na}) \\
                    m_{\infty}(V) &= \frac{\alpha_m(\sigma_{Na}, V)}
                        {\alpha_m(\sigma_{Na}, V) + \beta_m(\sigma_{Na}, V)} \\
                \alpha_m(\sigma_{Na}, V) &= -0.1 \frac{V + 29.7 - \sigma_{Na}}
                    {\exp(-0.1(V + 54.7 - \sigma{Na})) - 1} \\
                \beta_m(\sigma_{Na}, V) &= 4\exp(-\frac{V+54.7-\sigma_{Na}}{18})
            \end{aligned} $ \\ \rowcolor{Gray} 
        Persistent Sodium Currents ($I_{Na(P)}$) & $
                \begin{aligned}
                    I_{Na(P)} &= g_{Na(P)} \cdot m^3_{\infty}(\sigma_{Na(P)},
                    V) \cdot (V - V_{Na}) \\
                \end{aligned} $
            \\ \rowcolor{LightGray}
        Leak Current ($I_L$) &  $
            \begin{aligned}
                I_L &= g_L \cdot (V - V_L) \\
            \end{aligned} $ \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the neuron model}} 
    \label{Table:4}
\end{table}

\begin{landscape}
\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{1.5cm}lllll}
        \thickhline
        \multicolumn{5}{c}{Model Parameters} \\\thickhline \rowcolor{Gray}
        Currents Type  & Common &  Figure $1$ & Figure $2$ & Figure $3$ \\
        \thickhline \rowcolor{LightGray}
        Membrane Potential & $
            \begin{aligned}
                C_m &= 1 \mu F/cm^2 \\
                V_0 &= -74mV
            \end{aligned} $ & & & \\\rowcolor{Gray}
        T-Type Calcium Current & $
            \begin{aligned}
                \phi_h &= 2 \\
                V_{Ca} &= 120mV
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 1 mS/cm^2 \\
                \theta_h &= -81 mV \\
                k_h &= 6.25 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 0.3 mS/cm^2\\
                \theta_h &= -79 mV \\
                k_h &= 5 mV^{-1}
            \end{aligned} $ & $
            \begin{aligned}
                g_T &= 0.3 mS/cm^2\\
                \theta_h &= -75 mV \\
                k_h &= 5 mV^{-1}
            \end{aligned} $ \\\rowcolor{LightGray}
        Sag Current & $
            \begin{aligned}
                \phi_H &= 1 \\
                g_h &= 0.04 mS/cm^2 \\
                V_h &= -40 mV
            \end{aligned} $
        & & & \\\rowcolor{Gray}
        Hodgkin-Huxley Currents & $
            \begin{aligned}[l]
                g_K &= 30 mS/cm^2 \\
                V_K &= -80 mV \\
                \phi_n &= 28.5\\
                \sigma_K &= 10 \\
            \end{aligned} 
            \begin{aligned}[r]
                g_{Ca} &= 42 mS/cm^2 \\
                V_{Ca} &= 55 mV \\
            \end{aligned} $
            & $\sigma_{Na} = 3$ & $\sigma_{Na} = 6$ & $\sigma_{Na} = 6$
            \\\rowcolor{LightGray}
        Persistent Sodium Currents & $
            \begin{aligned}
                V_{Na(P)} &= 55 mV \\
                \sigma_{Na(P)} &= -5
            \end{aligned} $
            & $g_{Na(P)} = 9 mS/cm^2$ & $g_{Na(P)} = 9 mS/cm^2$ &
                $g_{Na(P)} = 9mS/cm^2$ 
            \\\rowcolor{Gray}
        Leak Current & & $
            \begin{aligned}
                g_L &= 0.1 mS/cm^2\\
                V_L &= -72 mV
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.12 mS/cm^2\\
                V_L &= -70 mV
            \end{aligned} $ & $
            \begin{aligned}
                g_L &= 0.08 mS/cm^2\\
                V_L &= -70 mV
            \end{aligned} $ \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Parameters}} 
    \label{Table:5}
\end{table}
\end{landscape}

@@

We simulated the model described in Table~\ref{Table:4} using the parameters
given in Table~\ref{Table:5} and the corresponding input (see
Table~\ref{Table:3} for three different cases. First, we verified 
that the model is able to generate different types of burst responses such
as in figure $1$ of the original article. We did not reproduce the entire 
diagram, instead we picked up five different cases from the original article
and we tested our implementation on these cases. Thus we applied a periodic 
current pulse of $-1 \mu A/cm^2$ amplitude at three different frequencies
(in the original article frequency is referred as $\frac{1}{P_0}$) $5Hz$, $8Hz$
and $10Hz$. The pulse is on for $p ms$ and the ratio $\frac{p}{P_0}$ is
defined, accordingly.
We chose the frequency and the on-duration of the pulse according to figure $1$
of the original article and such that we have a different type of burst response
for each ratio. The results are shown in Figure~\ref{Fig:1}. It is apparent that
the reference implementation can achieve the same behavior as the original
implementation. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.7\textwidth]{figs/Figure1.pdf}
    \caption{{\bfseries \sffamily Responses to rhythmic hyperpolarizations.}
        We stimulate the model with a periodic pulse with frequency
        $\frac{1}{P_0}$ and we record the response of the model. All the
        parameters for this simulation are given in Table~\ref{Table:3}. 
        {\bfseries \sffamily Blue} indicates a frequency $\frac{1}{P_0} = 10Hz$
        and a pulse duration $p = 10 ms$. A resting state activity is 
        generated.
        {\bfseries \sffamily Black} color shows the case where $\frac{1}{P_0} =
        10 Hz$ and $p = 40 ms$. In this case we get a single spike
        periodically. 
        {\bfseries \sffamily Red} color demonstrates a burst with two spikes,
        when the frequency of the periodic pulse is taken to be $\frac{1}{P_0}
        = 5 Hz$ and $p = 40 ms$. 
        {\bfseries \sffamily Cyan} curve shows burst responses consist in 
        three spikes. In this case $\frac{1}{P_0} = 8 Hz$ and $p = 75ms$. 
        {\bfseries \sffamily Magenta} curve indicates a burst periodical 
        response of four spikes per period. }
    \label{Fig:1}
\end{figure}
%%
In a second case, we used a steady current varying only its amplitude and 

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting
        and intermittent phase-locking
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
\usepackage{array}
\usepackage[export]{adjustbox}

\newcommand{\Rm}[1]{\mathrm{#1}}

@@

This work introduces a reference implementation of a neuron model for
thalamocortical relay neurons, proposed by X-J Wang, \cite{wang:1994}.
The model is conductance-based and takes advantage of an interplay between
a T-type calcium current and a non-specific cation sag current and thus, it
is able to generate spindle and delta rhythms. Another feature of this model
is the presence of an intermittent phase-locking phenomenon where action 
potentials of sodium take place in a non-periodic manner, despite the fact
that they are phase-locked to the periodic input current. Finally, the model
is capable of generating tonic spike patterns. The source code of
reference implementation is written in Python (Numpy, Scipy, Matplotlib,
and Scikit-image).

@@

In this section, a detailed description of the model is given following 
the paradigm of Nordlie et al, \cite{nordlie:2009}. Therefore, a brief
description of the model, equations, parameters, and inputs are given in
the form of tables.

Table~\ref{Table:1} provides a description of the model, Table~\ref{Table:2}
provides information about simulations duration and temporal integration time
steps, Table~\ref{Table:3} gives a glimpse of the input signals used in this work.
Table~\ref{Table:4} introduces the equations of the model and finally 
Table~\ref{Table:5} summarizes all the parameters for each figure (simulation).
The neuron model is conductance-based consisting of four differential equations
describing the dynamics of membrane potential and the kinetics of a T-Type
calcium current, a Sag current channel and a Potassium channel. The rest
currents are described by algebraic equations.
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- one neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Hodgkin-Huxley conductance-based \\\rowcolor{Gray}
        Channel Models & \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or periodic rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, channels activation, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{Table:1}
\end{table}
 %%  
The reference implementation has been done in a Python class (Python $3.5.1$)
along with Numpy (version $1.10.4$), Scipy (version $0.17.0$), Matplotlib
($1.5.1$) and Scikit-image (version $0.12.3$). The numerical integration
has been done using the \emph{ode} method of Scipy \emph{integrate} package.
Three different methods have been tested in this work (\emph{dopri5}, 
\emph{Adams}, \emph{BDF}, \cite{ascher:1998}). \emph{dopri5} is the closest
numerical method to the one used by the author in the original article (the
author has numerically integrated the system of the four ODEs by using a
fifth-order adaptive size Runge-Kutta method). \emph{BDF} and \emph{Adams}
provide similar numerical results as the first one, but they are
faster\footnote{The user has the option to choose one of the three methods
    during class instantiating. We tested all three methods comparing, spike
    times, amplitudes and the coefficient of variation using as threshold value
    $0\, \Rm{mV}$. Spike events were overlapping, and $CV \simeq 1.5$ for all
    three methods. The membrane potential amplitude was sometimes different
    for the same spike events, however that difference was not too high as
    Figure~\ref{Fig:1} shows (up to $4\, \Rm{mV}$ at maximum). Thus we decided
    to use the \emph{Adams} method.}.
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ccc}
        \thickhline
        \multicolumn{3}{c}{Simulation Time} \\ \thickhline
        Figure & Simulation Time ($\Rm{s}$) & Integration Step ($\Rm{ms}$) \\ 
        \rowcolor{LightGray}
        $1$ & $6$ & $0.05$ \\ \rowcolor{Gray}
        $2$ & $15\times period$, $2$ & $0.05$ \\ \rowcolor{LightGray}
        $3$ & $6$ & $0.05$ \\ \rowcolor{Gray} 
        $4$ & $1.5$, $1.5$, $1$ & $0.05$ \\ \rowcolor{LightGray} 
        $5$ & $5$ & $0.05$  \\ \rowcolor{Gray} 
        $6$ & $2.5$ & $0.05$  \\ \rowcolor{LightGray} 
        $7$ & $40$, $20$ & $0.05$  \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Time}}
    \label{Table:2}
\end{table}
%%

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure1.pdf}
    \caption{{\bfseries \sffamily Spike waveform.} Three integration methods:
    Runge-Kutta $5$ (\emph{dopri5}), \emph{Adams}, and \emph{BDF} where tested
    in order to identify potential numerical differences in our simulations
    (see text for more details). The amplitude for the three methods have no
    significant differences for the randomly picked up spike waveform shown in 
    this figure (in general we detected differences up to $5\, \Rm{mV}$, data
    not shown here). Continuous line -- \emph{dopri5}, dashed line -- \emph{Adams},
    and dashed-dotted line -- \emph{BDF}.}
    \label{Fig:1}
\end{figure}

All simulations ran on a Dell OptiPlex $7040$, equipped with a sixth
generation i$7$ processor, $8\, \Rm{GB}$ of physical memory and running Arch
Linux.
The total execution time of all simulations was $526$ minutes and the peak
consumed memory was $465\, \Rm{MB}$\footnote{Python memory
    profiler used (\url{https://pypi.python.org/pypi/memory_profiler}).}\@. 
    All the parameters used during simulations are given in Table~\ref{Table:5}. 
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{llcccc}
        \thickhline
        \multicolumn{6}{c}{Input} \\\thickhline
        Figure  & Type & Form & \parbox[t]{1.5cm}{Frequency
            ($\frac{1}{P_0}$, $\Rm{Hz}$)} & 
            \parbox[t]{1.5cm}{Duration ($p$, $\Rm{ms}$)} &
            \parbox[t]{1.5cm}{Amplitude ($\mu \Rm{A} / \Rm{cm}^2$)} \\
        \thickhline \rowcolor{LightGray}
        Figure~$1$ & Constant & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$-0.6$}
            \\\rowcolor{Gray}
        Figure~$2$ & Periodic & 
            \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} &
            \parbox[t]{1.1cm}{$5$, $10$} &
            \parbox[t]{1.1cm}{$10$, $40$} &
            \parbox[c]{0.3cm}{$-1.0$}
            \\\rowcolor{Gray}
        Figure~$3$ & Constant  & 
        \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
        -- & -- & \parbox[c]{0.3cm}{$+3.0$ \\ $3$ $0.0$ $-0.45$ $-0.455$
            $-0.47$ $-0.55$ $-0.6$ $-0.8$ $-1.3$ $-1.4$ $-2.1$} 
        \\\rowcolor{LightGray}
        Figure~$4$ & Pulse/Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & \parbox[c]{0.3cm}{100} & \parbox[c]{0.3cm}{$-1.25$ $0.25$ $-0.47$}
        \\\rowcolor{Gray}
        Figure~$5$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$-0.95$}
        \\\rowcolor{LightGray}
        Figure~$6$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$[-2,0]$}
        \\\rowcolor{Gray}
        Figure~$7$ & Constant  & 
            \includegraphics[width=0.1\textwidth]{figs/const.pdf} &
            -- & -- & \parbox[c]{0.3cm}{$[-2,0]$} \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the applied current
        $I_{\text{app}}$ }}
    \label{Table:3}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{1.5cm}ll}
        \thickhline
        \multicolumn{2}{c}{Neuron Model} \\\thickhline
        \rowcolor{Gray}
        Name  &  Thalamocortical relay neuron  \\ \rowcolor{LightGray}
        Type  &  Conductance-based neuron  \\ \rowcolor{Gray}
        Membrane Potential & $
            \begin{aligned}
                C_{\Rm{m}} \frac{dV(t)}{dt} &= -I_{\Rm{T}} - I_{\Rm{h}} - 
                I_{\Rm{Na}} - I_{\Rm{K}} - I_{\Rm{Na(P)}} - I_{\Rm{L}} +
                I_{\text{app}}
              \end{aligned}$ \\ \rowcolor{LightGray}
        T-Type Calcium Current ($I_T$) & $
            \begin{aligned}
                I_{\Rm{T}} &= g_{\Rm{T}} \cdot s^3_{\infty}(V)\cdot h \cdot
                (V-V_{\Rm{Ca}}) \\
                s_{\infty}(V) &= \frac{1}{1 + \exp(-\frac{V+65}{7.8})} \\
                \frac{dh(t)}{dt} &= \phi_h \frac{h_{\infty}(V) - h}{\tau_h(V)} \\
                h_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V-\theta_h}{k_h})} \\
                \tau_h(V) &= h_{\infty}\exp(\frac{V+162.3}{17.8}) + 20
            \end{aligned} $
            \\ \rowcolor{Gray}
        Sag Current ($I_h$) & $
            \begin{aligned}
                I_h &= g_h \cdot H^2 \cdot (V-V_h) \\
                H_{\infty}(V) &= \frac{1}{1 + \exp(\frac{V+69}{7.1})} \\
                \frac{dH(t)}{dt} &= \phi_H \frac{H_{\infty}(V) - H}{\tau_H(V)} 
            \end{aligned} $
            \\ \rowcolor{LightGray} 
        Hodgkin-Huxley Currents ($I_K$) and ($I_{Na}$) & $
            \begin{aligned}
                I_{\Rm{K}} &= g_K \cdot n^4 \cdot (V - V_{\Rm{K}}) \\
                \frac{dn(t)}{dt} &= \phi_n \frac{n_{\infty}(V) - n(t)}{\tau_n(V)} \\
                n_{\infty}(\sigma_{\Rm{K}}, V) &=
                \frac{\alpha_n(\sigma_{\Rm{K}}, V)}
                {\alpha_n(\sigma_{\Rm{K}}, V) + \beta_n(\sigma_{\Rm{K}}, V)} \\
                \tau_n(\sigma_{\Rm{K}}, V) &= \frac{1}{\alpha_n(\sigma_{\Rm{K}}, V)
                + \beta_n(\sigma_{\Rm{K}}, V)} \\
                \alpha_n(\sigma_{\Rm{K}}, V) &= 
                \frac{-0.01 (V + 45.7 - \sigma_{\Rm{K}})}{\exp(-0.1(V + 45.7 - \sigma_{\Rm{K}})) - 1} \\ 
                \beta_n(\sigma_{\Rm{K}}, V) &= 0.125 \exp(-\frac{V + 55.7 -
                    \sigma_{\Rm{K}}}{80}) \\
                I_{\Rm{Na}} &= g_{\Rm{Na}} \cdot m^3_{\infty}(\sigma_{\Rm{Na}}, V)
                \cdot (0.85 - n) \cdot (V - V_{\Rm{Na}}) \\
                m_{\infty}(V) &= \frac{\alpha_m(\sigma_{\Rm{Na}}, V)}
                {\alpha_m(\sigma_{\Rm{Na}}, V) + \beta_m(\sigma_{\Rm{Na}}, V)} \\
                \alpha_m(\sigma_{\Rm{Na}}, V) &= -0.1 \frac{V + 29.7 -
                    \sigma_{\Rm{Na}}}
                    {\exp(-0.1(V + 54.7 - \sigma{\Rm{Na}})) - 1} \\
                    \beta_m(\sigma_{\Rm{Na}}, V) &=
                    4\exp(-\frac{V+54.7-\sigma_{\Rm{Na}}}{18})
            \end{aligned} $ \\ \rowcolor{Gray} 
        Persistent Sodium Currents ($I_{Na(P)}$) & $
                \begin{aligned}
                    I_{\Rm{Na(P)}} &= g_{\Rm{Na(P)}} \cdot
                    m^3_{\infty}(\sigma_{\Rm{Na(P)}},
                    V) \cdot (V - V_{\Rm{Na}}) \\
                \end{aligned} $
            \\ \rowcolor{LightGray}
        Leak Current ($I_L$) &  $
            \begin{aligned}
                I_L &= g_L \cdot (V - V_L) \\
            \end{aligned} $ \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the neuron model}} 
    \label{Table:4}
\end{table}
%%

%%
\begin{landscape}
\begin{table}[!htbp]
    \centering
    \begin{tabular}{cccccccc}
        \thickhline
        \multicolumn{8}{c}{Model Parameters} \\\thickhline
        Figure & $V_0\, (\Rm{mV})$ & $g_T\, (\Rm{mS/cm^2})$ & $\theta_h\,
        (\Rm{mV})$ & $k_h\, (\Rm{mV^{-1}})$ & $\sigma_{Na}\, (\Rm{mV})$ &
        $g_L\, (\Rm{mS/cm^2})$ & $V_L\, (\Rm{mV})$ \\\rowcolor{LightGray}
        \thickhline
        $1$ & $-74$ & $1$ & $-79$ & $-5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $2$ & $-74$ & $1$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\\rowcolor{LightGray}
        $3$ & $-74$ & $0.3$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $4$ & $-72$/$-64$ & $1.0$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{LightGray}
        $5$ & $-74$ & $0.3$ & $-75$ & $5$ & $6$ & $0.08$ & $-70$ \\\rowcolor{Gray}
        $6$ & $-74$ & $1$/$0.7$ & $-79$ & $5$ & $6$ & $0.1$/$0.04$ & $-70$ \\\rowcolor{LightGray}
        $7$ & $-72$ & $0.3$/$0.25$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\
        \thickhline
        \multicolumn{8}{l}{Common Parameters} \\\rowcolor{Gray}
        \multicolumn{8}{c}{$C_m = 1\, \Rm{\mu F/cm^2}$, $\phi_h = 2$,
        $V_{\Rm{Ca}} = 120\, \Rm{mV}$, $\phi_H = 1$, $g_h = 0.04\,
        \Rm{mS/cm^2}$, $V_h = -40\, \Rm{mV}$, $g_{\Rm{K}} = 30\, \Rm{mS/cm^2}$,
        $V_{\Rm{K}} = -80\, \Rm{mV}$, $g_{\Rm{Ca}} = 42\, \Rm{mS/cm^2}$} \\\rowcolor{Gray}
        \multicolumn{8}{c}{$V_{\Rm{Ca}} = 55\, \Rm{mV}$, $\phi_{n} = 28.5$,
        $\sigma_{\Rm{K}} = 10\, \Rm{mV}$, $V_{\Rm{Na(P)}} = 55\, \Rm{mV}$,
        $\sigma_{\Rm{Na(P)}} = -5\, \Rm{mV}$, $g_{\Rm{Na(P)}} = 9 \,
        \Rm{mS/cm^2}$}
        \\\thickhline
    \end{tabular}
    \caption{\bfseries \sffamily Simulation Parameters}
    \label{Table:5}
\end{table}
\end{landscape}
%%

@@

We simulated the model described in Table~\ref{Table:4} using the parameters
given in Table~\ref{Table:5} and the corresponding input (see 
Table~\ref{Table:3}). First, we examined what is the response of the reference 
implementation to rhythmic hyperpolarization. In \cite{wang:1994} this is 
illustrated in Fig~$1$\footnote{From now and then all the 
    figures of the original article will be referred as Fig} of the original
article. 
Thus, we applied a periodic current pulse of $-1\,\Rm{\mu A/cm^2}$ amplitude at
several different frequencies ($\frac{1}{P_0}$ is the frequency in $\Rm{Hz}$
and $P_0$ is the corresponding period in $\Rm{ms}$) ranging from 
$0.1\,\Rm{Hz}$ to $15\,\Rm{Hz}$ with a resolution (discretization) of $30$ 
points. The same number of samples used for discretizing the duration for each 
frequency. The results are shown in Figure~\ref{Fig:2} left panel. Right panel
shows three different simulations of the reference implementation at specific
frequencies ($10,\, 5,\, 0.5\, \Rm{Hz}$) and rations $p/P_0$ ($0.1, 0.6, 0.6$),
respectively (crossed area in Figure~\ref{Fig:2} reflects the transient, which 
is omitted in the rest of the figures in this work). It is apparent that right
and left panels are in an agreement indicating that the reference model
produces reliable results. 
The author in \cite{wang:1994} shows in Fig~$1$ a shaded are where the number 
of spikes is $0.5$. This number appears if one computes the average of 
suprathreshold and subthreshold spikes in one period.
